---
title: "Package function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mypackage)
```

# Introduction

This package contains some functions used in labs.

## mybin function

The function takes in a sample size n, the number of iterations, and a probability of success p, and returns a barplot for the percentage of samples vs number of successes.

```{r}
mybin(iter=100, n=10, p=0.7)
```

## Myddt function

The function takes in a data frame and the name of some species, then returns a Length~Weight plot with a quadratic curve for the species and a named list of the original data frame, subsetted data frame, and a relative frequency table of River in the original data frame. The function is made with 

```{r}
library(dplyr)
library(ggplot2)
ddt = read.csv("DDT.csv")
buff = myddt(ddt, SPECIES="SMBUFFALO")
```

## mymaxlik function

This function finds the maximum likelihood estimate. It takes in a function, some data as a vector, and a range of values of unknown parameters as a vector, then returns a graph showing line of log likelihood and the maximum likelihood estimate, and a named list of the index, the maximum likelihood estimate, the log likelihood, and a vector of slopes.

```{r}
mymaxlik(x=c(3,3,4,3,4,5,5,4),param=seq(0,1,length=1000),lfun=function(x,param) log(dbinom(x,prob=param,size=20)),main="Binomial", cex.main=2)
```

## Scatterhist function

The function takes in at least two parameters, two vectors, and can also take in their labels. It then returns a histogram combined with a scatterplot. 

```{r}
library(graphics)

with(ddt, scatterhist(LENGTH, WEIGHT, xlab="LENGTH"))
```

